\vspace{-3em} \textbf{Occultation mapping of Io's surface in the near-infrared \\ I: Inferring static maps}

### 2021-03-04 paper/paper.tex
minor

Besides being useful for modeling secondary eclipses of volcanic Super-Earths, our model is also likely to be useful for modeling features on gaseous exoplanets with sparse surface features.
These will be much easier to observe with JWST  than Super-Earths because of their larger size and higher surface temperatures.
Even if the sparsity assumption is not valid for these types of planets the hybrid pixel/spherical harmonic model can be easily be used with a different set of priors more appropriate for these observations.
For example, a sensible prior for the surface of a fast rotating gaseous exoplanet might be requiring some degree of azimuthal symmetry for the inferred map.

\subsection{Future work}
This paper is a first step in a series of papers dedicated to probabilistic modeling of Io's surface. 
A major issue with the model presented in this work is that we cannot naturally account for the time variability of surface emission.
In Paper II in this series, we aim to fit an ensemble of light curves (occultations by Jupiter, mutual occultations and phase curves) with a generalized model which will enable us to infer a time-dependent map of the entire surface and quantify the time variability over time scales of decades.
A spatio-temporal map of volcanic emission spanning such a long timescale will help us better understand the global evolution of volcanism on Io. 
In addition to modeling global properties of volcanism of Io, it would also be interesting to constrain the time evolution of peak emission in Loki Patera with high accuracy in order to better understand the resurfacing process.

>>>>

Besides being useful for modeling secondary eclipses of volcanic Super-Earths, our model can be used for modeling surfaces of gaseous exoplanets with sparse features.
These will be much easier to observe with JWST  than Super-Earths because of their larger size and higher surface temperatures.
Even if the sparsity assumption is not valid for these types of planets the hybrid pixel/spherical harmonic model can be easily be used with a different set of priors more appropriate for these observations.
For example, a sensible prior for the surface of a fast rotating gaseous exoplanet might be requiring some degree of azimuthal symmetry for the inferred map.
\newline
\subsection{Future work}
This paper is a first step in a series of papers dedicated to probabilistic modeling of Io's surface. 
A major issue with the model presented in this work is that we cannot naturally account for the time variability of surface emission.
In Paper II in this series, we aim to fit an ensemble of light curves (occultations by Jupiter, mutual occultations and phase curves) with a generalized model which will enable us to infer a time-dependent map of the entire surface and quantify the time variability over time scales of decades.
A spatio-temporal map of volcanic emission spanning such a long timescale will help us better understand the global evolution of volcanism on Io. 
In addition to modeling global properties of volcanism of Io, it would also be interesting to constrain the time evolution of peak emission in Loki Patera with high accuracy in order to better understand the resurfacing process.
